Code used to generate paper results : Database comparison and CT characteristics

### 2024-10-03 Paper_code-Database_Comparison.Rmd
Update sizes

upset_text_size <- c(1.5, 1.5, 1.5, 1.5, 2, 2)
 #c(intersection size title, intersection size tick labels, set size title, 
 # set size tick labels, set names, numbers above bars)
```

@@

```{r CTdatabase_ours}
CTdatabase_ours <- Venn(list(CTexploreR = CT_genes$external_gene_name,
                             CTdatabase = CTdatabase_cleaned$external_gene_name))
gp <- VennThemes(compute.Venn(CTdatabase_ours))
gp[["Face"]][["11"]]$fill <-  "mediumaquamarine"
gp[["Face"]][["10"]]$fill <-  "darkseagreen1"
gp[["Face"]][["01"]]$fill <-  "lightsteelblue1"
gp[["Set"]][["Set2"]]$col <-  "paleturquoise4"
gp[["Set"]][["Set1"]]$col <-  "darkseagreen4"
gp[["SetText"]][["Set2"]]$col <-  "paleturquoise4"
gp[["SetText"]][["Set1"]]$col <-  "darkseagreen4"
plot(CTdatabase_ours, gp = gp)

@@

upset(upset_CTdatabase,
      text.scale = upset_text_size)
```

```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/CTdatabase_comparison.pdf"))
plot(CTdatabase_ours, gp = gp)
upset(upset_CTdatabase,
      text.scale = upset_text_size)
dev.off()
```

@@

upset_text_size_all <- c(1.5, 1.5, 1.5, 1.5, 2, 1)
 #c(intersection size title, intersection size tick labels, set size title, 
 # set size tick labels, set names, numbers above bars)
upset(upset_all_database,
      nsets = 6,
      nintersects = 50,
      text.scale = upset_text_size_all)

>>>>

upset_text_size <- c(2, 2, 2, 2, 3.5, 3.5)
 #c(intersection size title, intersection size tick labels, set size title, 
 # set size tick labels, set names, numbers above bars)
```

@@

```{r CTdatabase_ours}
CTdatabase_ours <- Venn(list(CTexploreR = CT_genes$external_gene_name,
                             CTdatabase = CTdatabase_cleaned$external_gene_name))
gp <- VennThemes(compute.Venn(CTdatabase_ours))
gp[["Face"]][["11"]]$fill <-  "mediumaquamarine"
gp[["Face"]][["10"]]$fill <-  "darkseagreen1"
gp[["Face"]][["01"]]$fill <-  "lightsteelblue1"
gp[["Set"]][["Set2"]]$col <-  "paleturquoise4"
gp[["Set"]][["Set1"]]$col <-  "darkseagreen4"
gp[["SetText"]][["Set2"]]$col <-  "paleturquoise4"
gp[["SetText"]][["Set1"]]$col <-  "darkseagreen4"
gp[["FaceText"]][["11"]]$fontsize <- 30
gp[["FaceText"]][["10"]]$fontsize <- 30
gp[["FaceText"]][["01"]]$fontsize <- 30
gp[["SetText"]][["Set2"]]$fontsize <-  30
gp[["SetText"]][["Set1"]]$fontsize <- 30
plot(CTdatabase_ours, gp = gp)

@@

upset(upset_CTdatabase,
      text.scale = upset_text_size, 
      mb.ratio = c(0.6, 0.4))
```

```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/CTdatabase_comparison.pdf"),
    paper = "a4r")
plot(CTdatabase_ours, gp = gp)
upset(upset_CTdatabase,
      text.scale = upset_text_size,
      mb.ratio = c(0.6, 0.4))
dev.off()
```

@@

upset_text_size_all <- c(2, 2, 2, 2, 3, 2)
 #c(intersection size title, intersection size tick labels, set size title, 
 # set size tick labels, set names, numbers above bars)
upset(upset_all_database,
      nsets = 6,
      nintersects = 50,
      text.scale = upset_text_size_all,
      mb.ratio = c(0.6, 0.4))
